### 2017-12-01 Chapter3/expts.tex
Latest on 24/11/2017
Latest on 26/11/2017
Latest on 27/11/2017
Latest on 1/12/2017

In this section, we conduct extensive empirical evaluations of EUCBV against several other popular MAB  algorithms. We use expected cumulative regret as the metric of comparison. The comparison is conducted against the following algorithms: KLUCB+ \citep{garivier2011kl}, DMED \citep{honda2010asymptotically}, MOSS \citep{audibert2009minimax}, UCB1 \citep{auer2002finite}, UCB-Improved \citep{auer2010ucb}, Median Elimination \citep{even2006action}, Thompson Sampling (TS) \citep{agrawal2011analysis}, OCUCB \citep{lattimore2015optimally}, Bayes-UCB (BU) \citep{kaufmann2012bayesian} and UCB-V \citep{audibert2009exploration}\footnote{The implementation for KLUCB, Bayes-UCB and DMED were taken from \citet{CapGarKau12}}. The parameters of EUCBV algorithm for all the experiments are set as follows: $\psi=\frac{T}{K^2}$ and $\rho =0.5$ (as in Corollary \ref{Result:Corollary:1}). Note that KLUCB+ empirically outperforms KLUCB (as shown in \citet{garivier2011kl}).

\begin{figure}[!h]
    \centering
    \begin{tabular}{cc}
    \setlength{\tabcolsep}{0.1pt}
    \subfigure[0.25\textwidth][Expt-$1$: $20$ Bernoulli-distributed arms ]
    %with $r_{i_{{i}\neq {*}}}=0.07$ and $r^{*}=0.1$
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		%legend style={legendshift=32pt},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.5)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter3/results/NewExpt/Expt1/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/KLUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/DMED01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/UCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/BU01_comp_subsampled.txt};
      	\legend{UCB-V,EUCBV,KLUCB+,MOSS,DMED,UCB1,TS,OCUCB,BU}      	
      	\end{axis}
      	\end{tikzpicture}
  		\label{fig:1}
    }
    &
    \subfigure[0.25\textwidth][Expt-$2$: $3$ Group Mean Setting ]
    %with $r_{i_{{i}\neq {*}:1-33}}=0.1$, $r_{i_{{i}\neq {*}:34-99}}=0.6$, $r^{*}_{i=100}=0.9$ and $\sigma_{i=1:100}^{2} = 0.3$
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
        %clip mode=individual,grid,grid style={gray!30},
       	grid=major,
       	clip=true,
  		legend style={at={(0.5,1.5)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter3/results/NewExpt/Expt2/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/KLUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/UCBR01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/UCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/BU01_comp_subsampled.txt};      	
      	\legend{UCB-V,EUCBV,KLUCB-G+,MOSS,UCB-Imp,UCB1,TS-G,OCUCB,BU-G}
      	\end{axis}
      	\end{tikzpicture}
   		\label{fig:2}
    }
    \end{tabular}
    \caption{A comparison of the cumulative regret incurred by the various bandit algorithms. }
    \label{fig:karmed}
    \vspace*{-1em}
\end{figure}
% For the purpose of performance comparison

@@

\begin{figure}[!h]
    \centering
    \begin{tabular}{cc}
    \subfigure[0.25\textwidth][Expt-$3$: Failure of TS]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		ylabel={Cumulative Regret},
		xlabel={timestep},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter3/results/NewExpt/Expt3/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/BU01_comp_subsampled.txt};
      	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
      	\end{axis}
      	\end{tikzpicture}
  		\label{fig:3}
    }
    &
    \subfigure[0.25\textwidth][Expt-$4$: $3$ Group Variance Setting]
    %with $r_{i_{{i}\neq {*}}}=0.05$ and $r^{*}=0.1$
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{Chapter3/results/NewExpt/Expt41/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/BU01_comp_subsampled.txt};
      	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
      	\end{axis}
        \end{tikzpicture}
        \label{fig:4}
    }
	\end{tabular}
	\label{fig:furtherExpt1}
    \caption{Further Experiments with EUCBV}
    \vspace*{-1em}
\end{figure}
%\vspace*{-0.5em}

>>>>

In this section, we conduct extensive empirical evaluations of EUCBV against several other popular MAB  algorithms. We use expected cumulative regret as the metric of comparison. The comparison is conducted against the following algorithms: KLUCB+ \citep{garivier2011kl}, DMED \citep{honda2010asymptotically}, MOSS \citep{audibert2009minimax}, UCB1 \citep{auer2002finite}, UCB-Improved \citep{auer2010ucb}, Median Elimination \citep{even2006action}, Thompson Sampling (TS) \citep{agrawal2011analysis}, OCUCB \citep{lattimore2015optimally}, Bayes-UCB (BU) \citep{kaufmann2012bayesian} and UCB-V \citep{audibert2009exploration}\footnote{The implementation for KLUCB, Bayes-UCB and DMED were taken from \citet{CapGarKau12}}. The parameters of EUCBV algorithm for all the experiments are set as follows: $\psi=\frac{T}{K^2}$ and $\rho =0.5$ (as in Corollary \ref{Result:Corollary:1}). Note that KLUCB+ empirically outperforms KLUCB (see \citet{garivier2011kl}).

\begin{figure}[!th]
    \centering
    \begin{tabular}{cc}
    \setlength{\tabcolsep}{0.1pt}
    \subfigure[0.25\textwidth][Expt-$1$: $20$ Bernoulli-distributed arms ]
    %with $r_{i_{{i}\neq {*}}}=0.07$ and $r^{*}=0.1$
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=12pt},
		%legend style={legendshift=32pt},
		}
        \begin{tikzpicture}[scale=0.7]
      	\begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.5)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter3/results/NewExpt/Expt1/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/KLUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/DMED01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/UCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt1/BU01_comp_subsampled.txt};
      	\legend{UCB-V,EUCBV,KLUCB+,MOSS,DMED,UCB1,TS,OCUCB,BU}      	
      	\end{axis}
      	\end{tikzpicture}
  		\label{fig:1}
    }
    &
    \subfigure[0.25\textwidth][Expt-$2$: $3$ Group Mean Setting ]
    %with $r_{i_{{i}\neq {*}:1-33}}=0.1$, $r_{i_{{i}\neq {*}:34-99}}=0.6$, $r^{*}_{i=100}=0.9$ and $\sigma_{i=1:100}^{2} = 0.3$
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=12pt},
		}
        \begin{tikzpicture}[scale=0.7]
        \begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
        %clip mode=individual,grid,grid style={gray!30},
       	grid=major,
       	clip=true,
  		legend style={at={(0.5,1.5)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter3/results/NewExpt/Expt2/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/KLUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/UCBR01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/UCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt2/BU01_comp_subsampled.txt};      	
      	\legend{UCB-V,EUCBV,KLUCB-G+,MOSS,UCB-Imp,UCB1,TS-G,OCUCB,BU-G}
      	\end{axis}
      	\end{tikzpicture}
   		\label{fig:2}
    }
    \end{tabular}
    \caption{A comparison of the cumulative regret incurred by the various bandit algorithms. }
    \label{fig:karmed}
    \vspace*{-1em}
\end{figure}
% For the purpose of performance comparison

@@

\begin{figure}[!h]
    \centering
    \begin{tabular}{cc}
    \subfigure[0.25\textwidth][Expt-$3$: Failure of TS]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=12pt},
		}
        \begin{tikzpicture}[scale=0.7]
      	\begin{axis}[
		ylabel={Cumulative Regret},
		xlabel={timestep},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter3/results/NewExpt/Expt3/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt3/BU01_comp_subsampled.txt};
      	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
      	\end{axis}
      	\end{tikzpicture}
  		\label{fig:3}
    }
    &
    \subfigure[0.25\textwidth][Expt-$4$: $3$ Group Variance Setting]
    %with $r_{i_{{i}\neq {*}}}=0.05$ and $r^{*}=0.1$
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=12pt},
		}
        \begin{tikzpicture}[scale=0.7]
        \begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{Chapter3/results/NewExpt/Expt41/UCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/EUCBV01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/MOSS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/TS01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/OCUCB01_comp_subsampled.txt};
		\addplot table{Chapter3/results/NewExpt/Expt41/BU01_comp_subsampled.txt};
      	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
      	\end{axis}
        \end{tikzpicture}
        \label{fig:4}
    }
	\end{tabular}
	\label{fig:furtherExpt1}
    \caption{Further Experiments with EUCBV}
    \vspace*{-1em}
\end{figure}
%\vspace*{-0.5em}
